Designing Modular Software: A Case Study in Introductory Statistics

### 2016-10-10 jcgs-paper-2016/paper.Rmd
Add to conclusion

`intRo` can be a powerful and effective tool for introductory statistics education. Its modular structure allows it to be flexible enough for many different applications and curriculums. Its ease-of-use allows the student to focus her attention on the statistics task at hand, rather than struggling with software licenses and confusing interface navigation. Reproducible code generated from each analysis can be used to spark an interest in R programming in those who might otherwise not be exposed to it.

@@

Regardless, tools that focus on usability and extensibility in statistics education, such as `intRo`, are sure to encourage the next round of innovators to be interested and excited about statistical computing.

>>>>

In this paper, we have outlined a framework for designing a web-based, modular, extensible system which reproduces user actions into R code. We believe that the development strategies we've outlined can and should be applied to other software systems, as each of these characteristics aids in the ease-of-use and functionality of the overall product. Although we present them in the context of an introductory statistics application, these ideas are generalizable and we hope that they will gain traction in many other modern software systems.

With regards to `intRo` itself, we believe it can be a powerful and effective tool for introductory statistics education. Its modular structure allows it to be flexible enough for many different applications and curriculums. Its ease-of-use allows the student to focus her attention on the statistics task at hand, rather than struggling with software licenses and confusing interface navigation. Reproducible code generated from each analysis can be used to spark an interest in R programming in those who might otherwise not be exposed to it.

@@

Regardless, tools that focus on usability and extensibility, such as `intRo`, are sure to encourage the next round of innovators to be interested and excited about statistical computing.
